% DISCRIPTION -->
% Title:   C, C++ Developer - Computer Games
% Address: peoplebank consult recruit
% http://www.seek.com.au/Job/analyst-programmer-developer-c-c-computer-games-tcp-ip-3d-linux-redhat/in/melbourne-cbd-inner-suburbs/18525213
% Contact: Kim Bonavia on 03 8080 7200
%
%* C+ and C++ development technologies 
%* 3D modelling and computer games development experience
%* TCP/IP communications development
%---

% RESUME -->
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here initiate the articale
%
% set the general style of the article 
\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\pagestyle{empty} 
%\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=2cm]{geometry}

% set page layout
%\addtolength{\hoffset}{-1cm}
%\addtolength{\textwidth}{2cm}

% set fonts
% - use times new roman font
%\usepackage{pslatex}
% - use Arial font
\renewcommand{\rmdefault}{phv} % Arial
\renewcommand{\sfdefault}{phv} % Arial

% use little space between list
\usepackage{mdwlist}

% enable comments
\usepackage{verbatim}
%\usepackage{paralist}

% set hyperreference package
%\usepackage{hyperref}
%\hypersetup{colorlinks=false}
%\urlstyle{same}

% define the title
%\title{Sylvia Liu}
%\author{1079 North Road, Hughesdale, VIC \and 61435690185}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here start the body of the article 
\begin{document}

% COVER LETTER -->
\begin{comment}
This is cover letter field.
\end{comment}
%---

% generate the title
%\maketitle
% count pages
%\mainmatter
% insert table contents
%\tableofcontents

\begin{center}
  \section*{Sylvia Liu}
  \begin{tabular}{l r}
    1079 North Road, Hughesdale, VIC 3166 & (043)5690185 \\
    \multicolumn{2}{c}{sylviaonlyone@gmail.com} \\
  \end{tabular}
\end{center}

\begin{comment}
\begin{tabular}{l l}
  Mobile:  & 0435690185 \\
  E-mail:  & sylviaonlyone@gmail.com \\
  Address: & Hughesdale, VIC 3166 \\
  \multicolumn{2}{l}{Australia Permanent Resident, 175 visa holder} \\
\end{tabular}
\end{comment}

% Profile -->
\section*{Profile}
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item 5 years C/C++ and 1 year JavaScript programming experience
  \item 1.5 years experience in web application development using TCP/IP protocols
  \item Trained on SDLC methodology, had basic but clear understanding of the whole process and more concentrated on implementing phase, served in both Waterfall and Agile teams for 6 years in total
  \item Experience in test-driven manner, design and implement unit-test and automated-test
  \item Acted as requirement manager, rich experience on customer facing communication, analysis and documentation
  \item Leaded a test team to achieve memory-leak test goal
  \item Always deliver tasks on time, for that earned great feedback from employers and customers
  \item Self-motivated, always enthusiasm on new techs, quick learner
  \item Rich experience in embedded Linux platform and Windows platform
\end{itemize*}

% Tech skills -->
\section*{Technical skills}
\begin{description*}
    \setlength\itemindent{0cm}
    \setlength\itemsep{0.4em}
  \item [Language:] expert in C/C++, good at JavaScript, XML, HTML, Perl, familiar with Shell, Python, SQL
  \item [Application:] GCC, C166, Makefile, Vim, gdb, git, SVN, SourceSafe, Visual Studio 2005, Rational Purify, Synergy, Lotus Notes, Citrix, QEMU, MIC2, VMware, Jira
  \item [Platform:] Linux and Windows
  \item [Design model:] MVC, observer, factory, visitor
  \item [Others Skills:] STL libraries, GTK+, UI design and dev., event-driven dev., test-driven dev., Agile/SCRUM
\end{description*}

% Experience -->
\section*{Experience}

\paragraph{Software Engineer in Elektrobit (Beijing)} (2007 $\sim$ 2010) \\*
Got SCRUM training from Nokia while working as an external employee.
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item Worked on MeeGo pre-study project, tracked MeeGo's activities on the community, made analysis and deposit knowledge of MeeGo, build development environment and deploy simulator for application development.
  \item Worked at Nokia's premise for S30 project as an external employee for UI development, including bug-fixing, trouble-shooting, system optimization and new products' porting. C/C++ program, S30 platform on Linux. As a scrum team member, co-operated smoothly with a large-scale of engineers from different sites in different roles.
  \item Developed a web-based tool for mobile system test management, Server-Client model, implemented by C++, JavaScript plus XUL, XML, HTML on Windows platform in the test-driven manner, and obeyed the Agile process model. Introduced ClearSilver into the web-page generation module successfully. Acted as the requirement manager as well to gathering requirements and made documentations.
\end{itemize*}

\paragraph{Software Engineer in Dalian Matsushita Communication Software Engineering Co., Ltd} (2004 $\sim$ 2007) \\*
A CMMI3 certified Japanese company that looks high upon accurate process control and documentation. Got Waterfall SDLC model training there and obtained a deep understanding of the manner as a practicer. 
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item As a key member and assistant project leader, developed GTK+ based mobile phone middle-ware on MontaVista Linux in C. Composed all level design documents, created and maintained unit-test and responded on version control using SourceSafe.
  \item Leaded a system test team for mobile phone software memory-leak test by using IBM Rational Purify on MontaVista Linux. Responded on Distributing tasks, gathering the error reports, analyzing and filtering the data and transferring to developers.
  \item Developed C++ coding-check tool for the whole R\&D department use, by studying the C++ Grammar, defining the structures and programming by C/C++ via VC 6.0 on Windows platform.
\end{itemize*}

% Education -->
\section*{Education}
Bachelor of Engineering, Dalian University of Technology, China, 2004

\begin{comment}
\begin{tabular}{l l}
  Duration:   & 2000 - 2004 \\
  University: & Dalian University of Technology \\
  Degree:     & Bachelor of Engineering \\
  Major:      & Electronic and Information Engineering \\
  Minor:      & International Economics and Trade \\
  Country:    & China \\
\end{tabular}
\end{comment}

\end{document}
%---
