% DISCRIPTION -->

% Title: Tester 
% Address: Brisbane http://ephox.com/about/careers
% Contact: online
%
% Agile evironment
% Open source tools
%---

% COVER LETTER -->
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here initiate the letter
%
% set the general style of the letter 
\documentclass[a4paper,11pt]{letter}
%\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
%\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

% - use Arial font
\renewcommand{\rmdefault}{phv} % Arial
\renewcommand{\sfdefault}{phv} % Arial

% use little space between list
\usepackage{mdwlist}

% enable comments
\usepackage{verbatim}
%\usepackage{paralist}

\begin{document}
\signature{Sylvia}
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left

\begin{letter}{ Ephox \\
  225 Montague Rd, Level 4, \\
  West End QLD 4101
  }

\begin{flushleft}
{\large\bf Sylvia Liu}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill 1079 North Road, Hughesdale, VIC 3166 \\
\hfill (04) 3569-0185 \\
\hfill sylviaonlyone@gmail.com
\end{flushright} 
\vfill % forces letterhead to top of page

\opening{Dear Sir or Madam:}
\noindent I see you are looking for a tester. 

\noindent I am attracted by your open source description. Actually, I have 6 years software development experience with plenty time working on Linux and using open source tools. I would like to concentrate my skills on making automating tools, it will be really a happy thing if I can get the job. I am enthusiasm to the open source and automating which make work and life easier.

\noindent My test related experience are: \\
 - Leaded a memory leak test team, using Purify to check system's memory leak. \\
 - Developed a Test Management Tool, which is web-based, in test-driven manner. \\
 - Made unit test for middle-ware development.

\noindent Also, I have experience using many different open source tools, like Perl, Python, Shell, Latex, etc. I used them to make automatic works. You can find some of my work recently updated on github: \emph{https://github.com/sylviaonlyone} 

\noindent For more details, you can find in my resume. Hope my skills will be helpful to you.

\closing{Yours Sincerely,}
%\ps{}
%\encl{}
\end{letter}
\end{document}
