% DISCRIPTION -->

% Title: Tester 
% Address: Brisbane http://ephox.com/about/careers
% Contact: online
%
% Agile evironment
% Open source tools
%---

% RESUME -->
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here initiate the articale
%
% set the general style of the article 
\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\pagestyle{empty} 
%\usepackage[top=1.5cm, bottom=1.5cm, left=1.5cm, right=2cm]{geometry}

% set page layout
%\addtolength{\hoffset}{-1cm}
%\addtolength{\textwidth}{2cm}

% set fonts
% - use times new roman font
%\usepackage{pslatex}
% - use Arial font
\renewcommand{\rmdefault}{phv} % Arial
\renewcommand{\sfdefault}{phv} % Arial

% use little space between list
\usepackage{mdwlist}

% enable comments
\usepackage{verbatim}
%\usepackage{paralist}

% set hyperreference package
%\usepackage{hyperref}
%\hypersetup{colorlinks=false}
%\urlstyle{same}

% define the title
%\title{Sylvia Liu}
%\author{1079 North Road, Hughesdale, VIC \and 61435690185}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here start the body of the article 
\begin{document}

% COVER LETTER -->
\begin{comment}
This is cover letter field.
\end{comment}
%---

% generate the title
%\maketitle
% count pages
%\mainmatter
% insert table contents
%\tableofcontents

\begin{center}
  \section*{Sylvia Liu}
  \begin{tabular}{l r}
    1079 North Road, Hughesdale, VIC 3166 & (04)35690185 \\
    \multicolumn{2}{c}{sylviaonlyone@gmail.com} \\
  \end{tabular}
\end{center}

% Profile -->
\section*{Profile}
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item Leaded a test team to achieve memory-leak test goal
  \item Developed Test Management Tool in test-driven manner
  \item 5 years development experience on Linux platform
  \item Enthusiasm to open source tools, and good skills on using bunch of them, like Perl, Shell, Latex, MIC2, etc.
  \item Proactive team player in Agile teams, willing to learn new things and happy to cooperate with people
  \item You can visit my github repository \emph{https://github.com/sylviaonlyone} to see some of my work. This resume is generated by Latex. 
\end{itemize*}

% Tech skills -->
\section*{Technical skills}
\begin{description*}
    \setlength\itemindent{0cm}
    \setlength\itemsep{0.4em}
  \item [Language:] expert in C/C++, good at JavaScript, XML, HTML, Perl, Shell familiar with Python, SQL
  \item [Application:] GCC, C166, Makefile, Vim, gdb, git, SVN, SourceSafe, Visual Studio 2005, Rational Purify, Synergy, Lotus Notes, Citrix, QEMU, MIC2, VMware, Jira
  \item [Platform:] Linux and Windows
  \item [Design model:] MVC, observer, factory, visitor
  \item [Others Skills:] STL libraries, GTK+, UI design and dev., event-driven dev., test-driven dev., Agile/SCRUM
\end{description*}

% Experience -->
\section*{Experience}

\paragraph{Software Engineer in Elektrobit (Beijing)} (2007 $\sim$ 2010) \\*
Elektrobit is a Finland company focuses on Wireless Solution providing. \\
I got SCRUM training from Nokia while working as an external employee.
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item Worked on MeeGo pre-study project, made analysis and deposit knowledge of MeeGo, build development environment and deploy simulator for application development.
  \item Worked at Nokia's premise for S30 project as an external employee for UI development, including bug-fixing, trouble-shooting, system optimization and new products' porting. C/C++ program, S30 platform on Linux. As a scrum team member, co-operated smoothly with a large-scale of engineers from different sites in different roles.
  \item Developed a web-based tool for mobile system test management, Server-Client model, implemented by C++, JavaScript plus XUL, XML, HTML on Windows platform in the test-driven manner, and obeyed the Agile process model. Introduced ClearSilver into the web-page generation module successfully. Acted as the requirement manager as well to gathering requirements and made documentations.
\end{itemize*}

\paragraph{Software Engineer in Dalian Matsushita Communication Software Engineering Co., Ltd} (2004 $\sim$ 2007) \\*
This is a branch company of Panasonic Mobile Phone in China.
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item As a key member and assistant project leader, developed GTK+ based mobile phone middle-ware on MontaVista Linux in C. Composed all level design documents, created and maintained unit-test and responded on version control using SourceSafe.
  \item Leaded a system test team for mobile phone software memory-leak test by using IBM Rational Purify on MontaVista Linux. Responded on Distributing tasks, gathering the error reports, analyzing and filtering the data and transferring to developers.
  \item Developed C++ coding-check tool for the whole R\&D department use, by studying the C++ Grammar, defining the structures and programming by C/C++ via VC 6.0 on Windows platform.
\end{itemize*}

% Education -->
\section*{Education}
Bachelor of Engineering, Dalian University of Technology, China, 2004 \\
 - Major in Electronic and Information Engineering \\
 - Minor in International Economics and Trade \\

\end{document}
%---
