% DISCRIPTION -->
%
% Title:    Software Developer   
% Location: Australia-VIC-Melbourn
% Job Code: 7377
% http://tbe.taleo.net/NA3/ats/careers/requisition.jsp?org=QUEST&cws=1&rid=5110&source=Indeed
%---

% RESUME -->
%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here initiate the articale
%
% set the general style of the article 
\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\pagestyle{empty} 

%\usepackage{pslatex}
% - use Arial font
\renewcommand{\rmdefault}{phv} % Arial
\renewcommand{\sfdefault}{phv} % Arial

% use little space between list
\usepackage{mdwlist}

% enable comments
\usepackage{verbatim}
%\usepackage{paralist}

% make newline in tables
\usepackage{multirow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Here start the body of the article 
\begin{document}

% COVER LETTER -->
\begin{comment}
Dear Sir/Madame,

I am a software engineer with 6 years C/C++ experience including 1.5 years web development experience. I think my rich skills will most match your requirements and add value to you with following skills:
- C++ expert
- Rich knowledge on Linux platform
- SOAP network programming experience
- Enthusiasm in open source software
- Agile team player
- test-driven development and robots lover
- Self-motivated and quick learner
- Rich working experience make me easy warm up in team work

Besides that, you can find more details in my attached resume.
Your description of the position really attracted me, and I am willing to work for such an exciting organization. Hope my abilities may contribute to you.

Thank you for considering my application.
Waiting to hear from you soon.

Yours sincerely,
Sylvia
\end{comment}
%---

\begin{center}
  \section*{Sylvia Liu}
  \begin{tabular}{l r}
    1079 North Road, Hughesdale, VIC 3166 & 61(43)5690185 \\
    \multicolumn{2}{c}{sylviaonlyone@gmail.com} \\
  \end{tabular}
\end{center}

% Profile -->
\section*{Profile}
%\newcommand{\minitab}[2][l]{\begin{tabular}{#1}#2\end{tabular}}
\begin{tabular}{ l  p{10cm} }
  \hline
  \multirow{3}{*}{C++ experience} 
  & Studied and analyze C++ Standard for project purpose \\ 
  & CGI server developing using STL \\
  & Mobile game developing using template, OO design \\

  \hline
  \multirow{8}{*}{Linux and Windows} 
  & Rich experience on Linux with plenty of depth \\
  & - Developed mobile software on MontaVista Linux \\
  & - Setup VMware Linux environment for project \\
  & - Built MeeGo development environment for project \\
  & - Familiar with git, shell, perl, vim, and similar tools on Linux \\
  & Also some Windows development experience \\
  & - Developed coding check tool on Windows with VC++ 6.0 \\
  & - Developed Test Management Tool on Windows \\

  \hline
  \multirow{1}{*}{Relational database systems}
  & Experience of using SQL Server 2005 for database design \\

  \hline
  \multirow{5}{*}{Network programming}
  & Developed web-based Test Management Tool \\
  & - C++ for CGI server \\
  & - Javascript plus XUL, XML, HTML, for client \\
  & - SQL server for database and Apache as HTTP server \\
  & - Agile team and test-driven development manner \\

  \hline
  \multirow{2}{*}{Automated builds and testing}
  & Implemented hourly automated build on MinGW \\
  & Wrote code in a test-driven manner \\

  \hline
  \multirow{3}{*}{Other experience}
  & Enthusiasm in open source projects \\
  & Experienced in web service protocol SOAP \\
  & Self-motivated and quick learner \\

  \hline
\end{tabular}

% Tech skills -->
\section*{Technical skills}
\begin{description*}
    \setlength\itemindent{0cm}
    \setlength\itemsep{0.4em}
  \item [Language:] expert in C/C++, good at JavaScript, XML, HTML, Perl, familiar with Shell, Python, SQL
  \item [Application:] GCC, C166, Makefile, Vim, gdb, git, SVN, SourceSafe, Visual Studio 2005, Rational Purify, Synergy, Lotus Notes, Citrix, QEMU, MIC2, VMware, Jira, SQL Server 2005
  \item [Platform:] Linux and Windows
  \item [Design model:] MVC, observer, factory, visitor
  \item [Others Skills:] STL libraries, GTK+, UI design and dev., event-driven dev., test-driven dev., Agile/SCRUM
\end{description*}

% Experience -->
\section*{Experience}

\paragraph{Software Engineer in Elektrobit (Beijing)} (2007 $\sim$ 2010) \\*
Got SCRUM training from Nokia while working as an external employee.
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item Worked on MeeGo pre-study project, tracked MeeGo's activities on the community, made analysis and deposit knowledge of MeeGo, build development environment and deploy simulator for application development.
  \item Worked at Nokia's premise for S30 project as an external employee for UI development, including bug-fixing, trouble-shooting, system optimization and new products' porting. C/C++ program, S30 platform on Linux. As a scrum team member, co-operated smoothly with a large-scale of engineers from different sites in different roles.
  \item Developed a web-based tool for mobile system test management, Server-Client model, implemented by C++, JavaScript plus XUL, XML, HTML on Windows platform in the test-driven manner, and obeyed the Agile process model. Introduced ClearSilver into the web-page generation module successfully. Acted as the requirement manager as well to gathering requirements and made documentations.
\end{itemize*}

\paragraph{Software Engineer in Dalian Matsushita Communication Software Engineering Co., Ltd} (2004 $\sim$ 2007) \\*
A CMMI3 certified Japanese company that looks high upon accurate process control and documentation. Got Waterfall SDLC model training there and obtained a deep understanding of the manner as a practicer. 
\begin{itemize*}
    \setlength\itemsep{0.4em}
  \item As a key member and assistant project leader, developed GTK+ based mobile phone middle-ware on MontaVista Linux in C. Composed all level design documents, created and maintained unit-test and responded on version control using SourceSafe.
  \item Leaded a system test team for mobile phone software memory-leak test by using IBM Rational Purify on MontaVista Linux. Responded on Distributing tasks, gathering the error reports, analyzing and filtering the data and transferring to developers.
  \item Developed C++ coding-check tool for the whole R\&D department use, by studying the C++ Grammar, defining the structures and programming by C/C++ via VC 6.0 on Windows platform.
\end{itemize*}

% Education -->
\section*{Education}
Bachelor of Engineering, Dalian University of Technology, China, 2004

\end{document}
%---
